### 2021-10-12 docs/paper/sections/4_implementation.tex

\begin{enumerate}[label=(\roman*)]
	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
	\item The \emph{CodeLens integration} provides quick access to a slice usage samples and is attached to the definition of each package member in the source code editor.
\end{enumerate}

>>>>

\begin{enumerate}[label=(\roman*)]
	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
	\item The \emph{CodeLens integration} provides quick access to a slice of usage samples and is attached to the definition of each package member in the source code editor.
\end{enumerate}
